Baseline centering problem

### 2018-12-13 paper/tangotd.tex

``Universal value function approximators'' do a bit of that, but only
with the left (ordinary) Bellman equation.

@@

>>>>

``Universal value function approximators'' (Schaul--Horgan--Gregor--Silver ICML 2015) do a bit of that, but only
with the left (ordinary) Bellman equation. It amounts to solving $\#S$
independent Bellman equations, and relying on the generalization
abilities of the network, but the right equation is not exploited at all.

@@

Another equation that might be enforced is commutation between
$P$ and $\Delta^{-1}$; it is expressed similarly to the above, but I do
not know if there's a gain. It might transfer left to right Bellman
equations.

$\green$ is basically a model of the world (summed over time). The
difference with ordinary model-based is: $\green$ is trained as a fixed
point, considering all timescales at once. In ordinary model-based, the
model $\tilde P$ obviously commutes with its iterates ($\tilde P^t\tilde
P=\tilde P\tilde P^t$), but does not provide an easy and accurate
representation of the occupation measure $\tilde \Delta^{-1}=\sum_t \tilde P^t$. So even in
the model-based case, the above might be useful.
